---
title: "ML Assignment 4"
author: "Abhinay Chiranjeeth Marneni"
date: "2022-11-01"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## loading library functions packages
```{r}
library(tidyverse)  
library(flexclust)
library(cluster)
library(factoextra) 
library(FactoMineR)
library(gridExtra)
library(ggcorrplot)
library(dplyr)
```

## Importing the Pharmaceuticals.csv file
```{r}
data<- read.csv("C:/Users/abhin/OneDrive/Documents/Assigments Buss 1sem/ML/Pharmaceuticals.csv") # import the data
view(data) # using view function to display the whole table 
head(data) # Using head function to view the 6rows of dataset
```
# A.Use only the numerical variables (1 to 9) to cluster the 21 firms. Justify the various choices made in 
conducting the cluster analysis, such as weights for different variables, the specific clustering algorithm(s) 
used, the number of clusters formed, and so on. 
```{r}
set.seed(450)
da <- data [,3:11]
summary(da)
```
```{r}
# To scale the data from the variables are measured using various weights throughout the rows
set.seed(450)
data1 <- scale(da)
row.names(data1) <- data[,1]
distance <- get_dist(data1)
fviz_dist(distance)
head(round(as.matrix(distance), 2),4)# To calculating the distance between the rows of data and viewing the distance matrix.
```
## To check the major variables, I using the correlation matrix method
```{r}
set.seed(450)
corr <- cor(data1)
ggcorrplot(corr, outline.color = "blue", lab = TRUE, hc.order = TRUE, type = "full") 
```
## The k-means algorithm can be used to manually adjust K numbers to observe how the dataset clusters. I've chosen k values at random from 2,3,4 and 5, and a restart value of 25.
```{r}
set.seed(450)
k2 <- kmeans(data1, centers = 2, nstart = 25) 
k3 <- kmeans(data1, centers = 3, nstart = 25) 
k4 <- kmeans(data1, centers = 4, nstart = 25) 
k5 <- kmeans(data1, centers = 5, nstart = 25) 
k2$size 
k3$size 
k4$size 
k5$size 
k21 <- fviz_cluster(k2, data = data1)
k31 <- fviz_cluster(k3, data = data1)
k41 <- fviz_cluster(k4, data = data1)
k51 <- fviz_cluster(k5, data = data1)
grid.arrange(k21,k31,k41,k51)
```
## Elbow Method 
```{r}
set.seed(450)
ebow <- vector()
for(i in 1:10) ebow[i] <- sum(kmeans(data1,i)$withinss)
plot(1:10, ebow , type = "b" , main = paste('Cluster of Companies') , xlab = "Number of Clusters", ylab="ebow")
```

## Silhouette Method
```{r}
set.seed(450)
fviz_nbclust(data1, kmeans, method = "silhouette")
```
## From above graph we find K clusters value "5"
```{r}
set.seed(450)
k5 <- kmeans(data1, centers = 5, nstart = 25)
fviz_cluster(k5, data = data1)
```

# B. Interpret the clusters with respect to the numerical variables used in forming the clusters. 
```{r}
print(k5)
da %>% mutate(Cluster = k5$cluster) %>% group_by(Cluster) %>% summarise_all("mean")
clusplot(data1,k5$cluster, main="Clusters",color = TRUE, labels = 2,lines = 0)
```
## From above plot and data the companies are group into a varous clusters
 
##Cluster 1: MRK,PFE,GSK and JNJ
##Cluster 2: ABT,AHM,AZN,BMY,LLY,NVS,SGP and WYE
##Cluster 3: AGN and PHA
##Cluster 4: AVE,ELN,MRX and WYE
##Cluster 5: BAY,CHTT and IVX


# C. Is there a pattern in the clusters with respect to the numerical variables (10 to 12)?
```{r}
# Displaying the matrix and combining the clusters with the non-selected features
da1 <- data[,c(1,12,13,14)]
da2 <- as.data.frame(list(k5$cluster))
da1$cluster <- da2[,c(1)]
da1 %>% arrange(desc(da1$cluster))
data2 <- data[12:14] %>% mutate(Clusters=k5$cluster)
ggplot(data2, mapping = aes(factor(Clusters), fill =Median_Recommendation))+geom_bar(position='dodge')+labs(x ='Clusters')
ggplot(data2, mapping = aes(factor(Clusters),fill = Location))+geom_bar(position = 'dodge')+labs(x ='Clusters')
ggplot(data2, mapping = aes(factor(Clusters),fill = Exchange))+geom_bar(position = 'dodge')+labs(x ='Clusters')
```
## the Median Recommendation and Cluster

# D.Provide an appropriate name for each cluster using any or all of the variables in the dataset.

## Cluster 1: Best Market
## Cluster 2: Uncontrolled
## Cluster 3: excellent
## Cluster 4: take a risk 
## Cluster 5: Workable