---
title: "ML Assignment 3"
author: "Abhinay Chiranjeetgh Marneni"
date: "2022-10-11"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#  Loading library functions Packages

```{r}
library(class)
library(caret)
library(ISLR)
library(dplyr)
library(gmodels)
library(ggplot2)
library(knitr)
library(e1071)
library(pROC)
```

# Importing the Uviversal bank.csv file and to exarct the data into  factor variables 

```{r}

data1<-read.csv("C:/Users/abhin/OneDrive/Documents/Assigments Buss 1sem/ML/UniversalBank.csv",header=TRUE)
head(data1)
data1$Personal.Loan <- as.factor(data1$Personal.Loan)
data1$Online <- as.factor(data1$Online)
data1$CreditCard <- as.factor(data1$CreditCard)
is.factor(data1$Personal.Loan)
is.factor(data1$Online)
is.factor(data1$CreditCard)

```

# Partition the collecting data
```{r}
set.seed(400)
data_partition<-createDataPartition(data1$Personal.Loan,p=.6,list=FALSE,times=1)
train<-data1[data_partition,]
valid<-data1[-data_partition,]
head(train)
head(valid)
```
# Normalizing the data
```{r}
norm <- preProcess(train[,-c(10,13,14)], method=c("center","scale"))
train_norm <-predict(norm,train)
valid_norm<- predict(norm,valid)
head(valid_norm)
head(train_norm)

```


# A. Generate a pivot table for the training data utilising Online as a column variable, CC and Loan as Variable 
```{r}

table_loan<-table(train_norm$CreditCard,train_norm$Personal.Loan,train_norm$Online)
View(table_loan)
```
# B.The probability of loan acceptance (Loan = 1) conditional on having a bank credit card (CC = 1) and being an active user of online banking services (Online = 1) = (47 /(473+47))=0.09038461538

# C.Making two pivot table for training data that can assist Online with Loan & Credit Card with Loan

## 1. Online with Loan
```{r}
table_1<-table(train_norm$Personal.Loan,train_norm$Online)
View(table_1)
```

## 2. CreditCard with Loan
```{r}
table_2<-table(train_norm$Personal.Loan,train_norm$CreditCard)
View(table_2)
```
## loan =1 probabaility of loan
```{r}
table_3<-table(train_norm$Personal.Loan)
prop<-prop.table(table_3)
View(prop)
```
# D. the table Caculations Based on Pivot Tables, Individual Probabilities CC Given Loan

## i. P(CC = 1 | Loan = 1) (the proportion of credit card holders among the loan acceptors) =85/288=0.2951

## ii. P(Online = 1 | Loan = 1)= 171/288=0.5937

## iii. P(Loan = 1) (the proportion of loan acceptors) =0.096

## iv. P(CC = 1 | Loan = 0)  =799/(799+1913)=0.2946

## v. P(Online = 1 | Loan = 0) =1629/(1629+1083)=0.6006

## vi. P(Loan = 0) =0.904

# E. Naive Bayes

## Naive Bayes = P(Loan=1/CC=1,Online=1) = P(CC=1/Loan=1)P(Online=1/Loan=1)P(Loan=1)/P(CC=1/Loan=1)P(Online=1/Loan=1)P(Loan=1)+P(CC=1/Loan=0)P(Online=1/Loan=0)P(Loan=0) =0.09514777745

## Naive Bayes Probability is  0.09514777745

# F. Compared of probabilities using a pivot table and naive bayes probability

## The Probability obtained using pivot table is 0.09038461538
## The Probability obtained using Naive bayes formula is 0.09514777745
## Calculation of increase the actual value of probability is 0.00476316207

# G.Applying the above-calculated values to determine the naive Bayes probability P(Loan = 1 | CC = 1, Online = 1)
```{r}

model<-naiveBayes(Personal.Loan~CreditCard+Online,data=train_norm)

model

``` 









